%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{blindtext}

\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={RESUME},
    bookmarks=true,
    pdfpagemode=FullScreen,
    }
    
\urlstyle{same}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Deepak kumar} % Your name
\address{Diamond Hostel-173, IIT(ISM) Dhanbad-826004   } % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(Ph.No. +91-8084842091, Email : deepakworld258566@gmail.com, linkedin : \url{https://www.linkedin.com/in/deepak785})} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Technology, Dhanbad} \hfill {\em July 2015 - Present} 
\\Integrated Master of Technology, Mathematics and Computing   
\\ CGPA: 8.60
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses}
\itab{\textbf{}} \tab{}  \tab{\textbf{}}
\\ \itab{Data Base Management System (AMC 16101)} \tab{}  \tab{Computer Networks (AMC 15103)}
\\ \itab{Project Management (MSC 52104)} \tab{}  \tab{Operation Research(s) (AMC 15105)} 
\\ \itab{Object Oriented Programming (AMC 13102)} \tab{}  \tab{Data Structures and Algorithms (AMC 14103)} 
\\ \itab{Computer Organization (AMC 14104)} \tab{} \tab{Operating System (AMC 15106)}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{RELEVANT EXPERIENCES}
\begin{rSubsection}{ACADEMIC PROJECTS}{November 2018-Present}{\textbf{AUTOMATED EMOTION ANALYSIS}}{}
\item Understanding Group Dynamics Using Automated Emotion Analysis of Group Discussions(\textbf{Python}).
\item Worked on building an automated \textbf{machine learned system} to predict sentiments and emotions of human statements, and extending it to understand group dynamics from conversations.
\item Open Sourced the Emotion and \textbf{Sentiment Analysis Toolkit} which I developed in the process to help prototyping emotion and sentiment analysis
\end{rSubsection}
\begin{rSubsection}{MACHINE LEARNING PROJECT}{May-August 2018}{\textbf{DEEP LEARNING FOR VISUAL QUESTION ANSWERING.}}{\textbf{}}{}

\item  Project aimed at constructing \textbf{Neural Network-based models} for Answering Open-ended questions about images. 
\item  Multiple methods used for combining the visual and audio features, and their effect on the performance was studied. The entire network (except the CNN for image features) is trained End-to-End.
\end{rSubsection}



%------------------------------------------------
\begin{rSubsection}{DESIGN AND DEVELOPMENT WORK}{}{GitHub ID : \url{https://github.com/deepak785}}{}
\item \textbf{College Campus Tour App (Nov-Jan 2017) :}
Worked in a team of six people and Built an application in \textbf{HackFest} 2017 at IIT(ISM) Dhanbad that help the student and parents to take 360 virtual tour of college campus 
\item \textbf{Card Game Simulator (Aug-Dec 2017) :} \textbf{Designed and Developed algorithm }with two of my friends in \textbf{C++} that \textbf{simulate} a game played by card sharp (professional gambler) at Carnivals
%\item \textbf{Password Generator (Aug-Dec 2017) :}  Wrote a program in python that generate a strong password that have mixed up of lowercase, number and symbols.It also asks the user how strong they want their password
\item \textbf{Admission Chance Predictor (May-Aug 2017) :} Built a prediction model in Octave using \textbf{Logistic Regression} that Predicts the chances of  admission of a candidate Based on marks of previous two tests.
\item \textbf{House Price Predictor (May-Aug 2017) :} Built a \textbf{Linear Regression model in Octave} for \textbf{prediction} of \textbf{house prices} by taking area of the house and number of bedrooms as the input .The program use data of recent sales of houses in Portland ,Oregon for training the algorithm. 
\item \textbf{IIT DHANBAD Android App Initiative (Aug-Dec 2016) : } Created and launched the IIT DHANBAD App for Android, an \textbf{Open Source initiative} to get all the college information into the hands of the students.
\end{rSubsection}
\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
\begin{rSection}{UNIVERSITY LEADERSHIP}
\begin{rSubsection}{Concetto - Technical and entrepreneurial Festival, IIT Dhanbad}{October 2018}{\textbf{Public Relations}}{}
\item Spearheaded a 2-tier team of 40 people to successfully conduct professional shows, exhibitions and talks.
\item \textbf{Organized} talks in Cocetto by eminent personalities like Sri Anjaneyulu Dodde (DC, Dhanbad) with more than 1000 attendees.
\item Successfully organized \textbf{technical events} like Auto expo, Space expo and Robowar together for the first time in Concetto .
\end{rSubsection}
\begin{rSubsection}{KARTAVYA-NGO}{August 2017-November 2018}{\textbf{ Technical Program Manager }}{}
\item Coordinating with team of 20 students responsible for facilitating technical education to the slum children. 
\item Responsible for creating awareness among students related to advancement in technology and involved in different \textbf{Group Project activities}. 
\item Organized sessions on Personality Development and Career Awareness by esteemed alumni for over 1600 students
\end{rSubsection}
\begin{rSubsection}{HOSTEL COMMITTEE}{November 2018-Present}{\textbf{Hostel Prefect}}{}
\item Responsible for maintaining discipline in the Diamond Hostel IIT (ISM) Dhanbad.
\item \textbf{Team Leader}, Coordinating with team of 16 students responsible for solving various issue related to safe drinking water, modification in mess menu etc.
\end{rSubsection}
\end{rSection}
\begin{rSection}{Achievements} \itemsep -2pt
\item  Won a bronze medal in 101 Hack 55, a programming contest conducted on Hackerrank by competing among 3600 participants (\url{https://www.hackerrank.com/Davidkeshri})
\item  Winner of the 24-hour \textbf{Hackathon} organized by Atkin, India and won a prize for the same.\item 2016-Present : Recipient of an annual \textbf{scholarship} of Rs.90,000 from Department of Electronics \& Information Technology, Government of India.
\item Ranked in National Top 0.2\% (amongst 1,200,000 candidates) in JEE Mains 2015 and Top 1\% (amongst 150,000 candidates) in IIT-JEE Advanced 2015 
\item Stood \textbf{First} in Bihar Talent Search Exam conducted by state government, competing against more than 1000 participants
\item Scored \textbf{10 CGPA} in scale of 10 in 10th std.CBSE Exam. 
\end{rSection}
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages(Experienced) &  C, C++, Java (Android),\\
Programming Languages(Familiar) &  Python, JavaScript, SQL, HTML, CSS\\
Software \& Tools & Android Studio, GIT, Matlab, Linux, Excel \\
Technology & Decision Trees, Logistic Regression, NLP, CNN \\

Areas of interests & Mobile App Design and Deep Learning.
\end{tabular}

\end{rSection}
\begin{rSection}{Extra-curricular Activities} \itemsep -3pt
\item Secured \textbf{First} in Chess competition and represented district in State Chess competition 
\item Secured {Third} position in the Group Discussion Organized by SME ISM Student Chapter   
\end{rSection}
 % \item Member, Athletics Team, IIT Kanpur. Attended Summer Sport Camp as a long jumper.
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %



\end{document}
